---
title: "dev_history.Rmd empty"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Tools to Build the Annual Study of NYC Squirrel data",
    Description = "The NYC Squirrel data includes the locations, fur coloration, activities, and bizarro behavior of over 2,000 City squirrels. The present package gives different tools to explore this dataset.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Sébastien Rochette")
# Use git
usethis::use_git()
usethis::use_build_ignore(".git")
```

# Check the validity of the entry dataset

Because my dataset may be updated regularly, I need to be sure nothing as changed in its structure. I will build a function that checks the content of some columns of the dataset for instance:  

+ Verify positions are in New York, around central Park
+ Verify there is only one color in `primary_fur_color`
  + A `+` in the column is a sign of multiple colours

```{r function-1, echo=TRUE}
#' Check data integrity
#'
#' @param x dataframe with at least colums "lat", "long" and "primary_fur_color"
#'
#' @return Original dataframe if all tests are good. Otherwise stops.
#' @export
check_data_integrity <- function(x) {
  # Verify points are in New York around Central Park
  all_coords_ok <- all(
    c(
      min(x[["lat"]]) > 40.76400,
      max(x[["lat"]]) < 40.80100,
      min(x[["long"]]) > -73.98300,
      max(x[["long"]]) < -73.94735
    )
  )
  if (!all_coords_ok) {stop("Not all data are in Central Park")}
  
  # Verify there is only one color in primary_fur_color.
  # A `+` in the column is a sign of multiple colours
  if (any(grepl("+", x[["primary_fur_color"]], fixed = TRUE))) {
    stop("There are multiple colors in some 'primary_fur_color'")
  }
  
  message("All tests are good !")
}
```

```{r examples-1, echo=TRUE}
# A working example
my_data_example <- data.frame(
  lat = c(40.77, 40.78),
  long = c(-73.95, -73.96),
  primary_fur_color = c("grey", "black")
)
check_data_integrity(my_data_example)
```

```{r tests-1, eval=TRUE, echo=TRUE}
my_data_example <- data.frame(
  lat = c(40.77, 40.78),
  long = c(-73.95, -73.96),
  primary_fur_color = c("grey", "black")
)
my_data_example_error <- data.frame(
  lat = c(40.77, 40.78),
  long = c(-73.95, -73.96),
  primary_fur_color = c("grey+blue", "black") # not unique color
)

test_that("check_data_integrity works correctly", {
  expect_message(check_data_integrity(my_data_example), "All tests are good !")
  expect_error(check_data_integrity(my_data_example_error), "multiple colors")
})
```


```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd", name = "Find the squirrels !")
# pkgdown
usethis::use_pkgdown()
pkgdown::build_site()
```

<!-- # Inflate your package -->

<!-- You're one inflate from paper to box. -->
<!-- Build your package from this very Rmarkdown using `fusen::inflate()` -->

<!-- - Verify your `"DESCRIPTION"` file has been updated -->
<!-- - Verify your function is in `"R/"` directory -->
<!-- - Verify your test is in `"tests/testthat/"` directory -->
<!-- - Verify this Rmd appears in `"vignettes/"` directory -->


```{r development-extra, eval=FALSE}
usethis::use_readme_rmd()
usethis::use_github_action_check_standard()
usethis::use_coverage()
usethis::use_github_action("test-coverage")
usethis::use_github_action("pkgdown")
```


