---
title: "Find the squirrels !"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Find the squirrels !}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(squirrels.fusen)
```

<!--

# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 


# Check the validity of the entry dataset

Because my dataset may be updated regularly, I need to be sure nothing as changed in its structure. I will build a function that checks the content of some columns of the dataset for instance:  

+ Verify positions are in New York, around central Park
+ Verify there is only one color in `primary_fur_color`
  + A `+` in the column is a sign of multiple colours


```{r examples-1, echo = TRUE}
# A working example
my_data_example <- data.frame(
  lat = c(40.77, 40.78),
  long = c(-73.95, -73.96),
  primary_fur_color = c("grey", "black")
)
check_data_integrity(my_data_example)
```

<!-- # Inflate your package -->

<!-- You're one inflate from paper to box. -->
<!-- Build your package from this very Rmarkdown using `fusen::inflate()` -->

<!-- - Verify your `"DESCRIPTION"` file has been updated -->
<!-- - Verify your function is in `"R/"` directory -->
<!-- - Verify your test is in `"tests/testthat/"` directory -->
<!-- - Verify this Rmd appears in `"vignettes/"` directory -->

